The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2011-10-17 shortRange.inhomo/writeDown/main.tex
backup before revision

Figure \ref{fig:tmp2} presents the real RMS force error (in green
square and log-scaled) in a system using a uniform cut-off raidus of $r_c^\ast =
7.5$. The number density distribution along $x$ direction is shown by
the solid red line for reference.  The error is comparatively constant
at the bulk liquid and gas region. In contrast, two paaks, which are
more than one order of maganitude larger than the force errors in bulk
regions, form at the interfacial region.  The estimated RMS force
error is presented by solid blue line.  The estimate follows the real
error very well at the interfacial region, but slightly over estimate
the error in the bulk regions.  Two components of the force error,
namely the homogeneity error and inhomogeneity error are presented in
Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
the bulk regions, the dashed blue line overlaps with the solid blue
line, that means the homogeneity error dominates.  In the interfacial
region, in the contrary, the inhomogeneity error dominate, because the
dotted blue line overlaps with the solid one.

@@

Comparing the results of the force correction method at $r_c^\ast =
3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
accuracy of the former method is worse than the later (see
Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than
the later, and surface tension is as good as the later (see
Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
% In the force correction simulation, the
% inhomogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the inhomogeneity error.
Since the homogeneity error dominates in the former simulation and the
inhomogeneity error dominates in the later, the above observation
indicates different natures of error play different roles in the
simulations.  The homogeneity error is actually the variation of the
corrected error force that has a vanished mean, see
Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
force may point to any direction with the same probability, and may be
cancelled by itself in a long time average.  The inhomogeneity error,
in contrast, stems from the non-vanishing mean value of the error
force, which is alway pointing at one certain direction (the opposite
direction of the density gradient), and has low  oppotunity to be
self-cancelled.

>>>>

Figure \ref{fig:tmp2} presents the real RMS force error (in green
square and log-scaled) in a system using a uniform cut-off raidus of $r_c^\ast =
7.5$. The number density distribution along $x$ direction is shown by
the solid red line for reference.  The error is comparatively constant
at the bulk liquid and gas region. In contrast, two peaks, which are
more than one order of maganitude larger than the force errors in bulk
regions, form at the interfacial region.  The estimated RMS force
error is presented by solid blue line.  The estimate follows the real
error very well at the interfacial region, but slightly over estimate
the error in the bulk regions.  Two components of the force error,
namely the homogeneity error and inhomogeneity error are presented in
Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
the bulk regions, the dashed blue line overlaps with the solid blue
line, that means the homogeneity error dominates.  In the interfacial
region, in the contrary, the inhomogeneity error dominate, because the
dotted blue line overlaps with the solid one.

@@

Comparing the results of the force correction method at $r_c^\ast =
3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
accuracy of the former method is a little worse than the later (see
Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than
the later, and surface tension is as good as the later (see
Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
% In the force correction simulation, the
% inhomogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the inhomogeneity error.
Since the homogeneity error dominates in the former simulation and the
inhomogeneity error dominates in the later, the above observation
indicates different natures of error play different roles in the
equilibrium densities.  The homogeneity error is actually the variation of the
corrected error force that has a vanished mean, see
Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
force may point to any direction with the same probability, and may be
cancelled by itself in a long time average.  The inhomogeneity error,
in contrast, stems from the non-vanishing mean value of the error
force, which is alway pointing at one certain direction (the opposite
direction of the density gradient), and has low  oppotunity to be
self-cancelled.
